Bandwidth-Aware Reconfigurable Memory Design with Hybrid Memory Technologies

### 2011-04-05 trunk/paper.tex

\noindent{}{\bf{Memory technology of each level.}} The memory technology with
the highest provided bandwidth within the given range of capacity of each level
is selected. In our case, SRAM, STT-RAM, and RRAM are selected as the L2, L3,
and L4 caches respectively. As a result, the overall provided bandwidth curve of
the on-chip memory system will appear to be an envelope line of all the
available memory technologies as shown in
Figure~\ref{fig:pbw-envelope}.\vspace{5pt}

\noindent{}{\bf{Capacity of each level.}} The maximum availabe capacity of each
level is determined by the cross point of two memory technologies. In our case,
the capacities of SRAM/L2, STT-RAM/L2, and RRAM/L4 are 2MB, 512MB, and 1GB
respectively. At the system initialization, the capacity of each level is
defined to be the maximum available capacity of the level. According to the
reqirement of different applications, the capacities can be reconfigured at
run-time to provide best performance. The memory space of each level can also be
reconfigured to form an internal level as shown in Figure~\ref{fig:hw-config}.
The hardware and software supports for reconfiguration will be presented in the
following sections.

@@

When the system is initially powered on,

>>>>

\noindent{}{\bf{Memory technology of each level.}} The memory technology with
the highest provided bandwidth within the given range of capacity of each level
is selected. In our case, SRAM, STT-RAM, and RRAM are selected as the L2, L3,
and L4 caches respectively. \vspace{5pt}

\noindent{}{\bf{Capacity of each level.}} The maximum availabe capacity of each
level is determined by the cross point of two memory technologies. In our case,
the capacities of SRAM/L2, STT-RAM/L2, and RRAM/L4 are 2MB, 512MB, and 1GB
respectively. At the system initialization, the capacity of each level is
defined to be the maximum available capacity of the level. According to the
reqirement of different applications, the capacities can be reconfigured at
run-time to provide best performance. The memory space of each level can also be
reconfigured to form an internal level as shown in Figure~\ref{fig:hw-config}.
The hardware and software supports for reconfiguration will be presented in the
following sections.\vspace{5pt}

The goal of such architecture design is to make use of different memory
technologies to configure an on-chip memory system with optimal provided
bandwidth over a range of capacities. As a result, the overall provided
bandwidth curve of the on-chip memory system will appear to be an envelope line
of all the available memory technologies as illustrated in
Figure~\ref{fig:pbw-envelope}. It is illustrated in this figure that the hybrid
memory system always provides the highest bandwidth over different capacities.

@@

Although the above hybrid memory system maintains the optimal provided bandwidth
curve over all the capacities, it does not garantee the best performance for
different applications with a variety of bandwidth requirements. The overall
provided bandwidth curve shown in Figure~\ref{fig:pbs-envelope} appears to be
monotonically decreasing. A specific application may have a bandwidth
requirement that can be mapped to a single point on the curve. To address this
issue, we dynamically reconfigure the memory space of each level corresponding
to the bandwidth requirement of each set of applications running on the system.
To be more aggressive, the reconfiguration is applied at the end of each given
time interval to accomodate different program phases of an application.
